An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-22 draft.tex
Images in pdf, changed ignore file
package algorithm
marble controller diagram

\usepackage{lineno,hyperref}
\usepackage{rotating}
\graphicspath{ {./images/} }

@@

\subsection{Controller Container} 
\label{controller}

@@

@@

Figure \ref{fig:experiment_flow} shows the workflow users can follow to run
experiments in EvoSwarm. The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm Developers can upload the container definition or images directly to
DockerHub. Another option is to upload the image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub.  Docker Compose
configuration files can reference these containers. When a user needs to deploy
the application, he or she needs to edit the Docker compose file to specify the
type and number of containers needed for the application.  The Docker compose
application is responsible for starting all the containers or downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script using the
experiment id to generate a collection of files containing all the data
generated by the experiment. The script generates these files in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper.  There is also a script to
generate the files needed by the COCO framework, which can generate standard
comparisons against other methods.

>>>>

\usepackage{lineno,hyperref}
\usepackage{rotating}
\usepackage{algpseudocode,algorithm}

\graphicspath{ {./images/} }

@@

\subsection{Controller Container} 
\label{controller}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{marble_controller}
    \caption{Marble diagram for the Reactive Python implementation of the Controller}
    \label{fig:marble_controller}
\end{figure}

@@

\begin{algorithm}
    \caption{<your caption for this algorithm>}
    \label{<your label for references later in your document>}
    \begin{algorithmic}[1]
            \Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
            \State $r\gets a\bmod b$
            \While{$r\not=0$}\Comment{We have the answer if r is 0}
            \State $a\gets b$
            \State $b\gets r$
            \State $r\gets a\bmod b$
            \EndWhile\label{euclidendwhile}
            \State \textbf{return} $b$\Comment{The gcd is b}
            \EndProcedure

    \end{algorithmic}
\end{algorithm}

@@

Figure \ref{fig:experiment_flow} shows the workflow users can follow to run
experiments in Evo\-Swarm. The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm Developers can upload the container definition or images directly to
DockerHub. Another option is to upload the image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub.  Docker Compose
configuration files can reference these containers. When a user needs to deploy
the application, he or she needs to edit the Docker compose file to specify the
type and number of containers needed for the application.  The Docker compose
application is responsible for starting all the containers or downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script using the
experiment id to generate a collection of files containing all the data
generated by the experiment. The script generates these files in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper.  There is also a script to
generate the files needed by the COCO framework, which can generate standard
comparisons against other methods.
